### 2023-03-23 resilience.tex
up

\begin{proposition}\label{general}
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-resilient iff $\Bad \subseteq \pred^*(\Safe)$.\\
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-bounded-resilient iff $\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-resilient.\\
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-$k$-resilient iff $\Bad \subseteq \pred^k(\Safe)$.
\end{proposition}

\begin{proof}
Resilient means that 
\end{proof}

@@

\begin{corollary}
The bounded resilience problem is decidable for WSTS with effective predbasis, $\Safe=\uparrow \Safe$
and $\Bad=\uparrow \Bad$.
\end{corollary}

\begin{theorem}\label{k-up-up}
The % three %uniform 
$k$-resilience problem is decidable for WSTS with effective predbasis, strong upward-compatibility, $\Safe=\uparrow \Safe$
and $\Bad=\uparrow \Bad$.
%	and \Bad is upward closed or downward closed.
\end{theorem}

\begin{proof}
Since $\Safe=\uparrow \Safe$ and
$\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS with strong upward-compatibility,  $\pred^k(\Safe)=\uparrow \pred^k(\Safe)$ for all $k \in \N$, and $\pred^k(\Safe)$ admits a finite basis $B_{\pred^k(\Safe)}$.
\end{proof}

@@

\begin{theorem}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and the predbasis hypothesis, and two finite sets: $I_{\Bad}$ and $Min_{\Safe}$.
The  $k$-resilience problem (kRP) is decidable.
 \end{theorem}

@@

\begin{proposition}
The resilience problem is undecidable for WSTS with \textcolor{red}{more than one minimal element}, $\Safe=\downarrow \Safe$
and $\Bad=\downarrow \Bad$.
\end{proposition}

@@

\begin{tabular}{ | l | c | c | c | r |}
\hline   \Safe~\Bad & $\uparrow$~ $\uparrow$~ & $\uparrow$~ $\downarrow$~ & $\downarrow$~ $\uparrow$~ & $\downarrow$~ $\downarrow$~ \\ \hline
   RP & Decidable (Theorem~\ref{up-up}) & Decidable (Theorem~\ref{down-up}) & ? Undecidable & Undecidable \\ \hline
   BRP & Decidable & ? Decidable (Theorem~\ref{down-up}) & ? & Undecidable \\ \hline
      kRP & Decidable (Theorem~\ref{k-up-up}) & Decidable & ? & Undecidable \\ \hline
 \end{tabular}

>>>>

\begin{proposition}[Reformulation]\label{reformulation}
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-resilient iff $\Bad \subseteq \pred^*(\Safe)$.\\
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-$k$-resilient iff $\Bad \subseteq \pred^k(\Safe)$.
\end{proposition}

\begin{proposition}\label{general}
\textcolor{red}{
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-bounded-resilient iff $\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-resilient}
\end{proposition}

\begin{proof}
Resilient means that ...
\end{proof}

@@

\begin{proposition}
In WSTS with strong compatibility and effective predbasis,  $\Safe=\uparrow \Safe$, the bounded resilience problem is equivalent to the resilience problem.
\end{proposition}

\begin{proof}
Since $\Safe=\uparrow \Safe$ and
$\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS with strong %upward-
compatibility, then $\pred^k(\Safe)= \uparrow~\pred^k(\Safe)$ for all $k \in \N$,
and there exists $K \in \N$ such that 
$\pred^k(\Safe) = \uparrow \pred^k(\Safe) = \uparrow \pred^*(\Safe) = \pred^*(\Safe)$.
Hence the equivalence.
\end{proof}

\begin{corollary}\label{B-up-up}
The bounded resilience problem is decidable for WSTS with effective predbasis,
strong compatibility
 $\Safe=\uparrow \Safe$
and $\Bad=\uparrow \Bad$.
\end{corollary}

\begin{theorem}\label{k-up-up}
The % three %uniform 
$k$-resilience problem is decidable for WSTS with effective predbasis, strong %upward-
compatibility, $\Safe=\uparrow \Safe$
and $\Bad=\uparrow \Bad$.
%	and \Bad is upward closed or downward closed.
\end{theorem}

\begin{proof}
Since $\Safe=\uparrow \Safe$ and
$\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS with strong %upward-
compatibility, then $\pred^k(\Safe)= \uparrow~\pred^k(\Safe)$ for all $k \in \N$, and $\pred^k(\Safe)$ admits a finite basis $B_{\pred^k(\Safe)}$. From a similar reasoning as above, the $k$-resilience problem is decidable.
\end{proof}

@@

\begin{theorem}\label{k-down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and the predbasis hypothesis, and two finite sets: $I_{\Bad}$ and $Min_{\Safe}$.
The  $k$-resilience problem (kRP) is decidable.
 \end{theorem}

@@

\begin{theorem}\label{down-down}
The resilience problem is undecidable for WSTS with \textcolor{red}{more than one minimal element}, $\Safe=\downarrow \Safe$
and $\Bad=\downarrow \Bad$.
\end{theorem}

@@

\begin{center}
\begin{tabular}{ | l | c | c | c | r |}
\hline   \Safe~\Bad & $\uparrow$~ $\uparrow$~ & $\uparrow$~ $\downarrow$~ & $\downarrow$~ $\downarrow$~ & $\downarrow$~ $\uparrow$~ \\ \hline
   RP & Decidable (Theorem~\ref{up-up}) & Decidable (Theorem~\ref{down-up}) & Undecidable (Theorem~\ref{down-down}) & \textcolor{red}{Undecidable} \\ \hline
   BRP & Decidable (Corollary~\ref{B-up-up}) &  Decidable (Theorem~\ref{down-up}) & Undecidable & ?? \\ \hline
      kRP & Decidable (Theorem~\ref{k-up-up}) & \textcolor{red}{Decidable} (Theorem~\ref{k-down-up}) & Undecidable & ?? \\ \hline
 \end{tabular}
\end{center}

\mathieu{En rouge quand il s'agit de conjectures}
